### 2018-06-18 readme.rmd
updated ppa-var wording
changes

The left column is analyses that have not been recoded, and the other three columns present the analyses for the three types of recoding. Feuda *et al.* 2017 reject the analyses that have not been recoded, all of which provide significant support for Ctenophora-sister, based on PP scores. These PP scores do not, however, uniformly indicate improved adequacy of recoded analyses over analyses that have not been recoded. Specifically, the ppa-conv analyses suggest that the analyses that have not been recoded are more adequate (ie, have a lower score) than the recoded analyses. This is the case for both the Chang and Whelan matrix. The impact of recoding on PP analyses therefore depends on the  PP statistic under consideration.

@@

*Figure 4 - Detailed examination of the analysis subset (indicated in upper right pane) that is the focus of the conclusions by Feuda et al. These include the six recoded CAT-GTR+G analyses with posterior predictive (PP) scores. The presented statistics for these six cells are posterior probability of Porifera-sister, Maxdiff (with lower scores indicating better convergence), and five PP scores (where lower absolute value indicates better model adequacy). Only one analysis provides significant support for Porifera-sister (shown in green). It is not the most adequate analysis by any of the PP scores, and showed the poorest convergence according to Maxdiff. Recodings are: K - KGB-6, D - Dayhoff-6, and S- SR-6.*

>>>>

The left column is analyses that have not been recoded, and the other three columns present the analyses for the three types of recoding. Feuda *et al.* 2017 reject the analyses that have not been recoded, all of which provide significant support for Ctenophora-sister, based on PP scores. These PP scores do not, however, uniformly indicate improved adequacy of recoded analyses over analyses that have not been recoded. Specifically, the ppa-conv analyses suggest that the analyses that have not been recoded are more adequate (ie, have a lower score) than the recoded analyses. This is the case for both the Chang and Whelan matrix. The ppa-var analyses indicate that that analyses that have not been recoded are more adequate than analyses that have been recoded with Dayhoff-6  and SR-6 recoding. The impact of recoding on PP analyses therefore depends on the  PP statistic under consideration.

@@

*Figure 4 - Detailed examination of the analysis subset (indicated in upper right pane) that is the focus of the conclusions by Feuda et al. These are the eight CAT-GTR+G analyses with posterior predictive (PP) scores. The presented statistics for these cells are posterior probability of Porifera-sister, Maxdiff (with lower scores indicating better convergence), and five PP scores (where lower absolute value indicates better model adequacy). Only one analysis provides significant support for Porifera-sister (shown in green). It is not the most adequate analysis by any of the PP scores, and showed the poorest convergence according to Maxdiff. Recodings are: K - KGB-6, D - Dayhoff-6, and S- SR-6.*
